Topological Equivariant Artist Model

### 2022-02-23 slides/main.tex
construction/maps to

\begin{comment}

@@

\begin{frame}{Measurable Visual Components}
    \begin{columns}
        \column{0.31\textwidth}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                \onslide*<1|handout:1>{\vfiberc}
                \onslide*<1|handout:1>{\arrow[r, hook]} \& 
                \onslide*<1|handout:1>{\vtotalc} 
                \onslide*<1|handout:1>{\arrow[d, "\pi"']} \\
                \& 
                \onslide*<1|handout:1>{\dbasec} 
                \onslide*<1|handout:1>{\arrow[u, "\vsectionc \in \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}"', bend right, pos=.5]}
            \end{tikzcd}
        \end{equation*}
        \column{0.69\textwidth}
    \only<1|handout:1>{
        \begin{description}[style=nextline]
            \item[\textcolor{total}{Data \vtotalc}]{continuity + visual fields}
            \item[\textcolor{base}{Continuity \dbasec}]{data continuity}
            \item[\textcolor{fiber}{components \vfiberc}] {visual components \cite{bertinIIPropertiesGraphic2011} of a graphic, e.g. x and y position, area, color, line thickness}
        \end{description}
        }
    \end{columns}
    \pause 
    \only<1|handout:1>{
        \begin{alertblock}{}
            \begin{description}[style=nextline]
                \item[\textcolor{section}{visual Components}]{$\cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \coloneqq \big\{\vsectionc: \opensetc\rightarrow \vtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\vsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$}
            \end{description}
        \end{alertblock}
    }
\end{frame}

\begin{frame}{Functor $\vchannelc: \dfiberc \rightarrow \vfiberc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc 
            \arrow[rr, "\vchannelc_{\dfiberc,\vfiber}"] 
            \arrow[rrdd, "{\vchannelc_{\dfiberc,{\vfiberc}^{\prime}}"', dotted] 
            \&  \& 
            \vfiberc \coloneqq \dfiberc^{\prime}  
            \arrow[dd, "\vchannelc_{{\dfiberc}^{\prime}, {\vfiberc}^{\prime}}"] \\
            \&  \& \\
            \&  \& \vfiberc^{\prime}                           
        \end{tikzcd}
    \end{equation*}
    \begin{alertblock}
        $\vchannelc$ is a functor s.t. if there exists a map ${\vchannelc}_{\dfiber, \vfiber}: \dfiber \mapsto \vfiber$ and 
        ${\vchannelc}_{{\dfiber}^{\prime}, {\vfiber}^{\prime}}: {\dfiber}^{\prime} \mapsto {\vfiber}^{\prime}$ then by composition there exists a map ${\vchannelc}_{\dfiberc, {\vfiberc}^{\prime}}: \dfiberc \rightarrow {\vfiberc}^{\prime}$
    \end{alertblock}
\end{frame}

\begin{frame}{Equivariant Data to Components: $\vchannel: \sheaf_{\dbasec,\dtotalc} \rightarrow \sheaf_{\dbasec, \vtotalc}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \arrow[rr, "\vchannelc"] \& \& 
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \\
             \& \opensetc 
             \arrow[lu, "{\sheafc_{\dbasec,\dtotalc}}" description, maps to] 
             \arrow[ru, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to] \& 
            \end{tikzcd}
    \end{equation*}

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc$ as a functor such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ \note{for all sections} 
    \end{description} 
\end{alertblock}
\end{frame}

\begin{frame}{Sample $\dfuncc$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
    \begin{table}[H]
        \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
            \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
            nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
            ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
            interval &  translation &  $\vchannel (\delement + c) = \vchannel(\delement) + \vchannel(c)$ \\
            ratio &  scaling &  $\vchannel(\delement* c) = \vchannel(\delement)*\vchannel(c) $\\ \bottomrule
        \end{tabularx}
    \end{table}
\end{frame}

\begin{frame}{Shared Components: $\vchannelc = \prod\limits_{i=0}^{n}\vchannelc_i$}
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc_a\times \dfiberc_b 
            \arrow[rr, "\vchannelc"] 
            \arrow[rd, "p_{\dfiberc}"] \& \& \vfiberc_a\times \vfiberc_b 
            \arrow[rd, "p_{\vfiberc}"] \& \\    \& \dfiberc_{a} \arrow[rr, "\vchannelc_{a}", dashed] \& \& \vfiberc_a \\
            \dfiberc_a\times \dfiberc_c 
            \arrow[rr, "\vchannelc^{\prime}"] \arrow[ru, "p_{\dfiberc^{\prime}}"'] \& \& {\vfiberc_a}^{\prime}\times {\vfiberc_c}^{\prime} \arrow[ru, "p_{\vfiberc^{\prime}}"'] \&           
            \end{tikzcd}
    \end{equation}
    \begin{alertblock}{Consistent Transformations \cite{hullmanKeeping2018}}
        if $p_{\dfiberc} = p_{\dfiberc^{\prime}}$ then $p_{\vfiberc}(\vchannelc(\dsectionc)) = p_{\vfiberc^{\prime}}(\vchannelc^{\prime}(\dsectionc^{\prime}))$ s.t. there exists a transformation $\vchannelc_a: \dfiberc_{a}\rightarrow \vfiberc_{a}$
    \end{alertblock}
\end{frame}

\begin{frame}{Combining Components}
    \begin{tikzcd}[ampersand replacement = \&]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[r, "\vchannelc", color=artist] \& 
    \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
    \arrow[r, "\vmarkc_*", color=artist] 
    \arrow[rr, "\vmarkc", bend left, color=artist] \& 
    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} \& 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[l, "\vindexpushc"', color=functor, dashed]\\ 
    \& \\ \& 
    \opensetc 
    \arrow[luu, "{\sheafc_{\dbasec, \dtotalc}}" description, maps to, color=sheaf] 
    \arrow[uu, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to, color=sheaf] 
    \arrow[ruu, "{\sheafc_{\dbasec, \gtotalc}}" description, maps to, color=sheaf] 
    \& \& 
    \opensetgc 
    \arrow[uu, "{\sheafc_{\gbasec, \gtotalc}}" description, maps to, color=sheaf] 
    \arrow[ll, "\vindexc"', dashed, color=functor]
    \end{tikzcd}

    \begin{alertblock}{Equivariance}
        \item[equivariance] $\delta(\vmarkc(\vchannelc\dfuncc_{\dtotalc}(\dsectionc))) = \dfuncc_{M}(\delta(\dsectionc))$ 
        \item[continuity] the assembly function $\vmarkc$ is defined as  
        \begin{equation}
        \vmarkc_*(\vsection(\dbasepointc))(\gbasepointc) = \vmarkc(\vsectionc(\vindex(\gbasepointc)))   
        \end{equation}
        such that there must exist a deformation retract $\vindexc:\gbasec \rightarrow \dbasec$ for all points $\gbasepointc \in \gbase$. 
    \end{alertblock}
\end{frame}

\begin{frame}{Components to Graphic}
    \begin{figure}
        \includegraphics[scale=.15]{../paper/figures/qhat.png}
    \end{figure}
\end{frame}
\end{comment}
\end{document}

>>>>

@@

\subsection{Measurable Visual Components $M$}

\begin{frame}{Measurable Visual Components}
    \begin{columns}
        \column{0.31\textwidth}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
                \onslide*<1|handout:1>{\vfiberc}
                \onslide*<1|handout:1>{\arrow[r, hook]} \& 
                \onslide*<1|handout:1>{\vtotalc} 
                \onslide*<1|handout:1>{\arrow[d, "\pi"']} \\
                \& 
                \onslide*<1|handout:1>{\dbasec} 
                \onslide*<1|handout:1>{\arrow[u, "\vsectionc \in \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}"', bend right, pos=.5]}
            \end{tikzcd}
        \end{equation*}
        \column{0.69\textwidth}
    \only<1|handout:1>{
        \begin{description}[style=nextline]
            \item[\textcolor{total}{Data \vtotalc}]{continuity + visual fields}
            \item[\textcolor{base}{Continuity \dbasec}]{data continuity}
            \item[\textcolor{fiber}{components \vfiberc}] {visual components \cite{bertinIIPropertiesGraphic2011} of a graphic, e.g. x and y position, area, color, line thickness}
        \end{description}
        }
    \end{columns}
    \pause 
    \only<1|handout:1>{
        \begin{alertblock}{}
            \begin{description}[style=nextline]
                \item[\textcolor{section}{visual components}]{$\cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \coloneqq \big\{\vsectionc: \opensetc\rightarrow \vtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\vsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}$}
            \end{description}
        \end{alertblock}
    }
\end{frame}

\begin{frame}{Data to Visual Transformation: $\vchannelc: \dsectionc \mapsto \vsectionc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vchannelc", color=artist, maps to] \& \& 
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \\
             \& \opensetc 
             \arrow[lu, "{\sheafc_{\dbasec,\dtotalc}}" description, maps to, color=sheaf] 
             \arrow[ru, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to, color=sheaf] \& 
            \end{tikzcd}
    \end{equation*}

    \begin{alertblock}{constraints} 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$
            \item[pointwise] $\vchannelc: \dsectionc(\dbasepointc) \mapsto \vsectionc(\dbasepointc) = \vchannelc: \vindexpullc\dsectionc(\gbasepointc) \mapsto \vindexpullc\vsectionc(\gbasepointc)$ when $\vindexc(\gbasepointc) = \dbasepointc$ 
    \end{description} 
\end{alertblock}
\end{frame}

\begin{frame}{Functor $\vchannelc: \dsectionc \mapsto \vsectionc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
            \arrow[rr, "\vchannelc_{\dfiberc,\vfiberc}", maps to, color=artist] 
            \arrow[rrdd, "{\vchannelc_{\dfiberc,{\vfiberc}^{\prime}}}"', dotted, maps to, color=artist] 
            \&  \& 
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \coloneqq \cgamma{\opensetc}{\dtotalc^{\prime}\restriction_{\opensetc}} 
            \arrow[dd, "\vchannelc_{{\dfiberc}^{\prime}, {\vfiberc}^{\prime}}", maps to, color=artist] \\
            \&  \& \\
            \&  \& \cgamma{\opensetgc}{\vtotalc^{\prime}}                           
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{$\vchannelc:\dfuncc_{\dtotalc} \mapsto \dfuncc_{\vtotalc}$: Stevens' Scales \cite{stevensTheoryScalesMeasurement1946}}
    \begin{table}[H]
        \begin{tabularx}{\textwidth}{|l|l|X|}\toprule
            \textbf{scale} & \textbf{group} & \textbf{constraint} \\\midrule
            nominal & permutation &  $\text{if } \delement_1 \neq \delement_2 \text{ then } \vchannel (\delement_1) \neq\vchannel(\delement_2)$\\
            ordinal &  monotonic & $\text{if } \delement_1 \leq \delement_2 \text{ then } \vchannel (\delement_1) \leq \vchannel(\delement_2)$\\
            interval &  translation &  $\vchannel (\delement + c) = \vchannel(\delement) + \vchannel(c)$ \\
            ratio &  scaling &  $\vchannel(\delement* c) = \vchannel(\delement)*\vchannel(c) $\\ \bottomrule
        \end{tabularx}
    \end{table}
\end{frame}

\begin{frame}{Shared Components: $\vchannelc = \prod\limits_{i=0}^{n}\vchannelc_i$}
    \begin{equation}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc_a\times \dfiberc_b 
            \arrow[rr, "\vchannelc", color=artist, maps to] 
            \arrow[rd, "p_{\dfiberc}", color=fiber] \& \& \vfiberc_a\times \vfiberc_b 
            \arrow[rd, "p_{\vfiberc}", color=fiber] \& \\    \& 
            \dfiberc_{a} 
            \arrow[rr, "\vchannelc_{a}", dashed, maps to, color=artist] \& \& \vfiberc_a \\
            \dfiberc_a\times \dfiberc_c 
            \arrow[rr, "\vchannelc^{\prime}", color=artist, maps to] 
            \arrow[ru, "p_{\dfiberc^{\prime}}"', color=fiber] \& \& 
            {\vfiberc_a}^{\prime}\times {\vfiberc_c}^{\prime} 
            \arrow[ru, "p_{\vfiberc^{\prime}}"', color=fiber] \&           
            \end{tikzcd}
    \end{equation}
    \begin{alertblock}{Consistent Transformations \cite{hullmanKeeping2018}}
        if $p_{\dfiberc} = p_{\dfiberc^{\prime}}$ then $p_{\vfiberc}(\vchannelc(\dsectionc)) = p_{\vfiberc^{\prime}}(\vchannelc^{\prime}(\dsectionc^{\prime}))$ s.t. there exists a transformation $\vchannelc_a: \dfiberc_{a}\rightarrow \vfiberc_{a}$
    \end{alertblock}
\end{frame}

\subsection{Visual Representations of Data}

\begin{frame}{Building a Visual Representation}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement = \&, column sep=small]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
        \arrow[rr, "\vchannelc", color=artist, mapsto] 
        \& \& 
        \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \& 
        \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
        \arrow[rr, "\vmarkc", color=artist] 
        \& \& 
        \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}\\
        \& \& \& \&  \& \\
        \& \opensetc 
        \arrow[luu, "{\sheafc_{\dbasec, \dtotalc}}" description, maps to, color=sheaf] 
        \arrow[ruu, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to, color=sheaf] 
        \& \& 
        \opensetc 
        \arrow[uu, "{\sheafc_{\dbasec, \vtotalc}}" description, maps to, color=sheaf]  
        \& \& 
        \opensetgc 
        \arrow[uu, "{\sheafc_{\gbasec, \gtotalc}}" description, maps to, color=sheaf] 
        \arrow[ll, "\vindexc"', color=functor]
        \end{tikzcd}
    \end{equation*}
    \begin{alertblock}{}
        \begin{description}[style=newline]
        \item[equivariance] $\delta(\vmarkc(\vchannelc\dfuncc_{\dtotalc}(\dsectionc))) = \dfuncc_{M}(\delta(\dsectionc))$ 
        \item[continuity] the assembly function $\vmarkc$ is defined as  
        \begin{equation}
        \vmarkc_*(\vsection(\dbasepointc))(\gbasepointc) = \vmarkc(\vsectionc(\vindex(\gbasepointc)))   
        \end{equation}
        such that there must exist a deformation retract $\vindexc:\gbasec \rightarrow \dbasec$ for all points $\gbasepointc \in \gbase$. 
        \end{description}
    \end{alertblock}
\end{frame}

\begin{frame}{Implementation Choices: $\vartistc_{\opensetc} = \vartistc_{\opensetgc}$}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement = \&, column sep=small]
        \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}  
        \arrow[r, "\vchannelc", maps to, color=artist] 
        \arrow[rrrr, "\vartistc_{\opensetgc}", Rightarrow, bend left, color=artist] \& 
        \cgamma{\opensetgc}{\vindexpullc\vtotalc\restriction_{\opensetgc}} \& 
        \cgamma{\opensetgc}{\vindexpullc\vtotalc\restriction_{\opensetgc}}  
        \arrow[rr, "\vmarkc^*", no head, Rightarrow, color=artist] \&  \& 
        \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}  
        \arrow[dd, "\vindexpushc", color=functor] \\
        \& \& \& \& \\
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}  
        \arrow[uu, "\vindexpullc", color=functor] 
        \arrow[r, "\vchannelc", maps to, color=artist] 
        \arrow[rrrr, "\vartistc_{\opensetc}", Rightarrow, bend right, color=artist] 
        \& 
        \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}  
        \arrow[uu, "\vindexpullc"', color=functor] \& 
        \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}
        \arrow[rr, "\vmarkc_*", Rightarrow, color=artist] 
        \arrow[uu, "\vindexpullc", color=functor] 
        \arrow[rruu, "\vmarkc", Rightarrow, color=artist] 
        \&  \& 
        \cgamma{\opensetgc}{\vindexpushc\gtotalc\restriction_{\opensetc}}
    \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{comment}
\begin{frame}{Components to Graphic}
    \begin{figure}
        \includegraphics[scale=.15]{../paper/figures/qhat.png}
    \end{figure}
\end{frame}
\end{comment}
\end{document}
